\prefacesection{Acknowledgments}

Mentorship by Peter Vincent, Patrice Castonguay, and David Williams was essential for my involvement in the intellectually stimulating topic of high order methods. David's tenacity, talent, and example helped me keep the passion for modeling and simulation alight. The work of Guido Lodato served as an inspiration for many of the topics of this thesis. Jonathan Bull's application of high order methods to turbulent flows served as guidance for the selection of capabilities that I would like to see in a Navier-Stokes solver.

Prof. Antony Jameson provided me with an invaluable environment of intellectual freedom framed by his sharing of pioneering ideas and insightful recommendations. His mastery of numerical analysis and crispness of communication are traits I shall strive to emulate.

Feedback and questions by Prof. Juan Alonso and Prof. Charbel Farhat have helped me contextualize the contributions in this dissertation in the larger scopes of Aerospace Engineering and Computational Fluid Dynamics. Comments by Prof. Parviz Moin and Prof. Brian Cantwell have encouraged my desire to apply the methods discussed here to simulations relevant to the understanding of flow physics.

Friendship and comradeship with Abhishek Sheshadri, Kartikey Asthana, Jerry Watkins II, Josh Romero, Jacob Crabill, and David Manosalvas made it enjoyable working in the Aerospace Computing Laboratory. I relied on their knowledge and eagerness to help to move past theoretical and implementation hurdles.

Support for this work was provided by the Aeronautics and Astronautics Departmental Fellowship and the Air Force Office of Scientific Research under grant \# FA9550-14-1-0186, monitored by Dr. Fariba Fahroo.
